EpisoDAS - DAS-based Password Generation \\ using Episodic Memories

### 2018-01-21 paper/AVI2018/paper.tex
...

\begin{document}
\title{EpisoDAS - DAS-based password generation \\
using episodic memories}
% \titlenote{Produces the permission block, and copyright information}

@@

\keywords{Passwords, visual passwords, user authentication, episodic memories, draw-a-secret}

@@

We introduce a simple and powerful visual interaction technique for
managing strong passwords.
%
Passwords have been used for qauthentication for decades, but
appropriate handling of passwords is difficult because people can
easily forget passwords and they can be easily cracked.
%
To make the authentication process easier, various visual interaction
methods have been proposed, including the DAS (draw-a-secret)
method. Using DAS, users can log into various services just by drawing
a secret pattern on the screen.
%
Using a DAS-based authentication method, users can quickly log into a
service without typing a password. However, remembering complex secret
patterns can be as difficult as remembering passwords. We developed
EpisoDAS, with which users can generate strong passwords based on
their secret episodic memories with a simple DAS interface.
%
users can use secret patterns for authentication, based on their
secret episodic memories which they cannot easily forget.

@@

However, password-based authentication is still the most convenient
and widely deployed method \cite{Bonneau:ReplacePasswords}, and is not
expected to disappear any time soon \cite{Herley:2009:PSS:1601990.1602010}.
%
To tackle this problem,
we have been proposing the \textit{EpisoPass} password generator with which 
users can generate strong passwords easily
based only on a user's secret and unforgettable episodic memories \cite{Masui:EpisoPass}.

@@

\begin{figure}[H]
  \centerline{\includegraphics[width=13cm,bb=-250 -100 1272 1014]{figures/episopass.png}}
  \caption{EpisoPass}
  \label{EpisoPass}
\end{figure}

@@

\begin{enumerate}
\item A user registers multiple question texts related to their own personal
secret unforgettable episodic memories. For each question they must provides
a single correct answer and multiple additional incorrect answers.

@@

\item EpisoPass shows the questions and answers to the user allowing
them to select the correct answer for each question.
Based on the user's selections,
EpisoPass substitutes characters in the seed string and generates a
strong password candidate string.
After selecting all of the correct answers,
the user copies the calculated string
and registers it as the password for the service.
\end{enumerate}

@@

For the people who don't like to use passwords for authentication,
various types of authentication methods have been proposed.
Especially, visual authentication methods
like graphical passwords\cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords}
and Draw-a-Secret (DAS) \cite{Jermyn:1999:DAG:1251421.1251422} are promising approaches, because
people can remember visual patterns easier than passwords.

% \begin{figure}[H]
%   \includegraphics[width=8cm,bb=0 0 448 351]{figures/Dejavu.png}
%   \caption{D\'{e}j\`{a} Vu}
%   \label{fig:sample}
% \end{figure}

\begin{figure}
  % \includegraphics[width=8cm,bb=0 0 840 792]{figures/DAS.png}
  % \includegraphics[width=8cm,bb=0 0 320 321]{figures/DASexample.jpg}
  \includegraphics[width=12cm,bb=0 0 1000 667]{figures/AndroidLock.jpg}
  \caption{Pattern lock for Android.}
  \label{AndroidLock}
\end{figure}

Visual authentication methods have better characteristics than
password-based authentication, but
they are either more fragile to attacks
or remembering is difficult.

We propose a new visual password generation system \textit{EpisoDAS},
which have the advantages of both EpisoPass and DAS-based methods.

@@

EpisoDAS is a visual authentication interface
based on the user's episodic memories.
Like EpisoPass,
EpisoDAS displays a list of questions to the user and
asks the user to choose the most appropriate answers
from the candidate answers.
EpisoDAS then generates a password string based on the user's selections.
%
% with which users can generate strong password based on their
% memory of visual patterns and episodic memories.
% Users can either select answers based on the user's secret episodic memories or
% draw a secret pattern represented by the pattern of selected answers.
% 
% Thus, users can recognize EpisoDas as a DAS system or
% use it as an implementation of EpisoPass.
%
The candidate answers are shown to the user as a grid of buttons,
and the user can select the most appropriate answer to each question
by clicking one of the buttons in the grid.

If the location of the series of correct answers form a special
pattern that the user can remember, the user can select
correct answers quickly just like using other DAS systems.

@@

\begin{figure}[H]
  \includegraphics[width=12cm,bb=0 0 1398 1060]{figures/EpisoDAS1.jpg}
  \caption{First question and answers shown on EpisoDAS.}
  \label{EpisoDAS1}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=12cm,bb=0 0 1396 1062]{figures/EpisoDAS2.jpg}
  \caption{Second question and answers.}
  \label{EpisoDAS2}
\end{figure}

If he remembers that he had a bad time at Los Angeles
after reading the question in Figure \ref{EpisoDAS2},
he would click ``Los Angeles'' and proceed to the third question.

The contents and the order of the questions
do not depend on the user's actions, and
the user cannot tell whether he has selected a right answer.

After repeating the slection process ten times,
the user can get his password
calculated from his selections (Figure \ref{Result}).

\begin{figure}[H]
  \includegraphics[width=10cm,bb=0 0 1160 468]{figures/result.png}
  \caption{Generated password}
  \label{Result}
\end{figure}

Users can select correct answers not only by clicking each button,
but by draggin the pointing device on the buttons.
%
If the series of button locations form a special pattern,
% If the series of buttons are aligned next to each others,
the user can drag the pointing device like
Figure \ref{draw} instead of clicking ten buttons,
and quickly generate a password.
%
The order of candidate answers change according to the drag or click action,
and the user can mix the dragging and clicking actions
at any point.
The user can either click ``Boston'' and ``Los Angeles'' one by one or
click on ``Boston'' and move the pointing device downward to select
``Los Angeles'' without releasing the mouse button or releasing the
pen or finger from the surface of the tablet computer.

\begin{figure}[H]
  \includegraphics[width=12cm,bb=0 0 1356 1046]{figures/draw.png}
  \caption{Drawing a secret pattern on EpisoDAS}
  \label{draw}
\end{figure}

The drawing action by the user is close to the actions
used on DAS systems.
Users can quickly generate his password for authentication
just by drawing a pattern on the EpisoDAS screen.

EpisoDAS can be used for generating passwords for any kind of systems and
services, but it is most useful when used to log in to a Web service
on a Web browser.
Figure \ref{Amazon} shows how a user can use EpisoDAS when
he wants to log in to Amazon.com.
If the EpisoDAS extension is installed on the browser,
an EpisoDAS window appears when the user enters his
email address and clicks the password field at Amazon.com.
After selecting answers by drawing a secret pattern on the EpisoDAS window,
a password for Amazon is generated and pasted
into the password field, making the user to log in without typing any password.

@@

\begin{figure}[H]
  \includegraphics[width=12cm,bb=0 0 1092 1026]{figures/Amazon.png}
  \caption{Login to Amazon.com}
  \label{Amazon}
\end{figure}

The data used in the above example is retrieved from the EpisoDAS database
on the Web, using the name of the service (e.g. \texttt{Amazon})
and the user id (e.g. \texttt{john@example.com}).

\section{Registration}

@@

\begin{figure}[H]
  \includegraphics[width=12cm,bb=0 0 1832 1180]{figures/JohnEpisodes.png}
  \caption{EpisoPass window}
  \label{JohnEpisodes}
\end{figure}

After selecting the correct answers
(``Boston'', ``Los Angeles'', etc.) on the EpisoPass editor page,
the user can click the ``DAS'' button on the top-right portion of the
EpisoPass page to specify his DAS patten.

@@

If the user wants to use a U-shape as the secret pattern,
he can begin drawing the shape shown in Figure \ref{DASRegister}
on the registration window.
%
After registering the pattern, the candidate answers for the EpisoPass is
shuffled so that the series of correct answers represent the specified pattern.

@@

Questions and answer candidates can be edited interactively on the
EpisoPass editor page (Figure \ref{EpisoPass}) and arbitrary
strings can be specified as questions and answer candidates.
However, creating many questions and answer candidates is not a
trivial task, because
people usually feel it difficult to recall secret episodes.
%
To help people easily create EpisoPass questions and answers,
we provide a special page for easy problem creation
(Figure \ref{Easy}).

@@

EpisoDAS browser extension is very useful, but creating the extension
is cumbersome because there is no standard login form for
Web services.
%
The browser extension should first detect that the Web page is a login page
of a Web service (e.g. Amazon),
and then it should be able to get the ID of the user
and know where the result of EpisoDAS calculation should be pasted.
%
Commercial password managers\cite{OnePassword,Dashlane,MilPass,LastPass,KeyPass,NortonIDSafe,IDManager}
are usually well integrated with Web browsers,
and EpisoDAS should also be evolved so that
the browser extension works on many Web services.

>>>>

\begin{document}
\title{EpisoDAS - DAS-based Password Generation \\
using Episodic Memories}
% \titlenote{Produces the permission block, and copyright information}

@@

\keywords{Passwords; visual passwords; user authentication;
  episodic memories; draw-a-secret.}

@@

We introduce a simple and powerful visual interaction technique for
managing strong passwords.
%
Passwords have been used for authentication for decades, but
appropriate handling of passwords is difficult because people can
easily forget passwords and they can be easily attacked.
%
To make the authentication process easier, various visual interaction
methods have been proposed, including the DAS (draw-a-secret)
method. Using DAS, users can log into various services just by drawing
a secret pattern on the screen.
%
Using a DAS-based authentication method, users can quickly log into a
service without typing a password, but remembering complex secret
patterns is as difficult as remembering passwords.
%
We developed \textit{EpisoDAS}, with which users can generate strong passwords
based on their secret episodic memories with a simple DAS interface.
%
users can use secret patterns for authentication, based on their
secret episodic memories that they cannot easily forget.

@@

However, password-based authentication is still the most convenient
and widely deployed method \cite{Bonneau:ReplacePasswords}, and is not
expected to disappear any time soon \cite{Herley:2009:PSS:1601990.1602010}.
%
To tackle this problem,
we have been proposing the \textit{EpisoPass} password generator \cite{Masui:EpisoPass}
with which users can generate strong passwords easily
based only on a user's secret and unforgettable episodic memories.

@@

\begin{figure}[t]
  % \centerline{\includegraphics[width=13cm,bb=-250 -100 1272 1014]{figures/EpisoPass0.png}}
  \centerline{\includegraphics[width=13cm,bb=-250 -100 1524 1286]{figures/EpisoPass1.png}}
  \caption{An EpisoPass page for \textsf{John@example.com}. John can edit questions and answers, enter a seed string,
  and a password is generated based on the selections.}
  \label{EpisoPass}
\end{figure}

@@

\begin{enumerate}
\item A user registers multiple question texts related to their own personal
secret unforgettable episodic memories. For each question they must provide
a single correct answer and multiple additional incorrect answers.

@@

\item EpisoPass shows the questions and answers to the user allowing
them to select the correct answer for each question.
Based on the user's selections,
EpisoPass substitutes characters in the seed string and generates a
strong password candidate string.
After selecting all of the correct answers,
the user copies the calculated string
and uses it as the password for the service.
\end{enumerate}

@@

For the people who don't like to use passwords for authentication,
various types of authentication methods have been proposed.
Especially, visual authentication methods
like graphical passwords \cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords}
and Draw-a-Secret (DAS) \cite{Jermyn:1999:DAG:1251421.1251422} are promising approaches, because
people can remember visual patterns easier than passwords.
%
Visual authentication methods have better characteristics than
password-based authentication, but
they are sometimes fragile to attacks or memorization is difficult.

We propose a new visual password generation system \textit{EpisoDAS}
that posesses the advantages of both EpisoPass and DAS-based methods.

\begin{figure}[t]
  % \includegraphics[width=8cm,bb=0 0 840 792]{figures/DAS.png}
  % \includegraphics[width=8cm,bb=0 0 320 321]{figures/DASexample.jpg}
  % \includegraphics[width=10cm,bb=0 0 1000 667]{figures/AndroidLock.jpg}
  \includegraphics[width=10cm,bb=-60 0 940 667]{figures/AndroidLock.jpg}
  \caption{An example DAS system. (``Pattern lock'' for Android)}
  \label{AndroidLock}
\end{figure}

@@

EpisoDAS is a visual authentication interface
based on the user's episodic memories.
Like EpisoPass,
EpisoDAS displays a list of questions to the user,
asks the user to choose the most appropriate answer from the candidate answers,
and generates a password string based on the user's selections.
%
% with which users can generate strong password based on their
% memory of visual patterns and episodic memories.
% Users can either select answers based on the user's secret episodic memories or
% draw a secret pattern represented by the pattern of selected answers.
% 
% Thus, users can recognize EpisoDas as a DAS system or
% use it as an implementation of EpisoPass.
%
The candidate answers are shown to the user as a grid of buttons,
and the user can select the most appropriate answer to each question
by clicking one of the buttons in the grid.
%
If the location of the series of correct answers form a special
pattern that the user can remember, the user can select
correct answers quickly just like using other DAS systems.

@@

\begin{figure}[t]
  \includegraphics[width=10cm,bb=-60 0 1338 1060]{figures/EpisoDAS1.jpg}
  \caption{First question and candidate answers shown on EpisoDAS.}
  \label{EpisoDAS1}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=10cm,bb=-60 0 1336 1062]{figures/EpisoDAS2.jpg}
  \caption{Second question and answers.}
  \label{EpisoDAS2}
\end{figure}

If he remembers that he had a bad time at Los Angeles,
% after reading the question in Figure \ref{EpisoDAS2},
he would click ``Los Angeles'' and proceed to the third question.

The contents and the order of the questions
do not depend on the user's actions, and
the user cannot tell whether he has selected a right answer.
%
After repeating the slection process ten times,
the user can get his password
calculated from his selections (Figure \ref{Result}).

\begin{figure}
  \includegraphics[width=10cm,bb=0 0 1160 468]{figures/result.png}
  \caption{Generated password.}
  \label{Result}
\end{figure}

Users can select correct answers not only by clicking each button,
but by draggin the pointing device on the buttons.
%
If the series of button locations form a special pattern,
% If the series of buttons are aligned next to each others,
the user can drag the pointing device like
Figure \ref{draw} instead of clicking ten buttons,
and quickly generate a password.
%
The order of the list of candidate answers change according to the
drag or click action,
and the user can mix the dragging and clicking actions at any point.
The user can either click ``Boston'' and ``Los Angeles'' one by one or
click on ``Boston'' and drag the pointing device downward to select
``Los Angeles'' without releasing the mouse button or releasing the
pen or finger from the surface of the tablet computer.

\begin{figure}[H]
  \includegraphics[width=12cm,bb=0 0 1356 1046]{figures/draw.png}
  \caption{Drawing a secret pattern on EpisoDAS.}
  \label{draw}
\end{figure}

The drawing action by the user is close to the actions
used on other DAS systems.
Users can quickly generate his password for authentication
just by drawing a pattern on the EpisoDAS screen.

EpisoDAS can be used for generating passwords for any kind of systems and
services, but it is most useful when it is used to log into a Web service.
Figure \ref{Amazon} shows how a user can use EpisoDAS when
he wants to log in to Amazon.com.
If the EpisoDAS extension is installed on the browser,
an EpisoDAS window appears when a user enters their
email address and clicks the password field.
After selecting answers by drawing a secret pattern on the EpisoDAS area,
a password for Amazon is generated and pasted
into the password field, making the user to log in without typing a password.

@@

\begin{figure}[t]
  \includegraphics[width=12cm,bb=0 0 1092 1026]{figures/Amazon.png}
  \caption{Using EpisoDAS on Amazon.com login page.
    When the user clicks the password field, EpisoDAS window automatically appears
    and a password is generated and pasted to the field after drawing a
    secret pattern.}
  \label{Amazon}
\end{figure}

The data used in the above example is retrieved from the EpisoDAS database
on the Web, using the name of the service (\texttt{Amazon})
and the user id (\texttt{john@example.com}).

\section{Data Registration}

A user has to register a DAS pattern and
Q-A database before using EpisoDAS.

@@

% \begin{figure}[H]
%   \includegraphics[width=12cm,bb=0 0 1832 1180]{figures/JohnEpisodes.png}
%   \caption{EpisoPass window}
%   \label{JohnEpisodes}
% \end{figure}

After selecting the correct answers
(``Boston'', ``Los Angeles'', etc.) on the EpisoPass editor page (Figure \ref{EpisoPass}),
the user can click the ``DAS'' button on the top-right portion of the
page to proceed to specify their DAS patten.

@@

If the user wants to use a U-shape as the secret pattern,
he can draw the shape shown in Figure \ref{DASRegister}
on the DAS registration window.
%
After registering the pattern, the candidate answers for the EpisoPass is
shuffled so that the series of correct answers represent the specified pattern.

@@

Questions and answer candidates can be edited interactively on the
EpisoPass editor page (Figure \ref{EpisoPass}) and arbitrary
strings can be specified as questions and answer candidates.
However, creating many questions and answer candidates is
time-consuming and hard task, because
people usually feel it difficult to recall old secret episodes.
%
To help people easily create EpisoPass questions and answers,
a support page can be used for easy problem creation
(Figure \ref{Easy}).

@@

EpisoDAS browser extension is very useful, but creating the extension
is cumbersome because there is no standard login form for
Web services.
%
The browser extension should first detect that the Web page is a login page
of a Web service (e.g. Amazon),
and then it should be able to get the ID of the user
and know where the result of EpisoDAS calculation should be pasted.
%
Commercial password managers\cite{OnePassword,Dashlane,LastPass,KeyPass,NortonIDSafe,IDManager}
are usually well integrated with Web browsers,
and EpisoDAS should also be evolved so that
the browser extension works on many Web services.
